Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex
latest correction after the clas comments

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value at given $Q^2$ and 
$W$~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$, 
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing a series 
of constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in FIG.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. Our final asymmetries have been corrected for this 
contamination in the form of
$A_{LU~\text{corrected}}~=~\frac{1}{1~-~\text{contamination~percentage}}~A_{LU~\text{measured}}$. 
The $\pi^0$ contamination was estimated using detector simulation and 
experimental data. From simulation, we calculated the ratio ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  Then in 
each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
experimental DVCS events were calculated as $N = N^{ep\rightarrow 
e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework. To explore this idea, we constructed the ratio of $A_{LU}$ for bound 
protons to that on a free proton target.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries that are independent of $t$ for a bound proton compared to 
the free proton. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium-modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. Our 
results show that an important nuclear effect is missing from the existing 
models in order to explain this strong quenching of the BSA. More theoretical 
developments will be needed to identify the origin of this quenching, in 
particular it will be important to differentiate initial from final state 
effects and how they can affect the DVCS asymmetries.

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value at given $Q^2$ and 
$W$~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$, 
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in FIG.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. Our final asymmetries have been corrected for this 
contamination in the form of
$A_{LU~\text{corrected}}~=~\frac{A_{LU~\text{measured}}}{1~-~\text{contamination~percentage}}$.  
The $\pi^0$ contamination was estimated using detector simulation and 
experimental data.  From simulation, we calculated the ratio ($R = 
N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then in 
each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
experimental DVCS events were calculated as $N = N^{ep\rightarrow 
e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework. To explore this idea, we constructed the ratio of $A_{LU}$ for bound 
protons to that on a free proton target.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries that are independent of $t$ for a bound proton compared to 
the free proton. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium-modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. Our 
results show that an important nuclear effect is missing from the existing 
models in order to explain this strong quenching of the BSA. More theoretical 
developments will be needed to identify the origin of this quenching, in 
particular it will be important to differentiate initial from final state 
effects and how they affect the DVCS asymmetries.
